Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-06-21 local-capability-machine/local-capability-machine.tex
Added call macro - section could still use a bit of polishing.

>>>>

Possible implementation. We will use $\texttt{malloc $r$ $n$}$ and \texttt{rclear $\bar{r}$} (defined below). Assume $\bar{r_{\var{priv}}} = r_{\var{priv},1}, \dots, r_{\var{priv},n}$
  malloc r_t ... // ... is the size of activation record
// store private state in activation record
  store r_t r_priv,1
  store r_t r_priv,2
  store r_t r_priv,n
// store old pc
  lea r_t1 ... // ... is the offset to return address
  store r_t r_t1
// store activation record
  store r_t encode(i_1)
  store r_t encode(i_m)
  lea r_t1 k //  k is m-1, i.e. the offset to the first instruction of the activation code.
  restrict r_t1 encodePermPair((Local,e))
  move r_0 r_t1
  rclear R // R = RegisterName - {r,pc,r_0,r_args}
Activation record. The instructions correspond to $i_1,\dots,i_m$ in the above.
  move r_t pc
// load private state
  lea r_t r_t1
  load r_priv,1 r_t
  load r_priv,2 r_t
  load r_priv,n r_t
// load old pc
  load pc r_t
